---
title: "R Notebook"
output: html_notebook
---

```{r}
setwd("C:/Users/nezfa/OneDrive/Ambiente de Trabalho/Unidades Curriculares/Data Mining 2/Projeto/Code/Recommendations")
library(recommenderlab)
library(readr)
library(dplyr)
library(tidyverse)
```


```{r}
# Read the dataset
chicago_crimes <- read_csv("chicago_crimes_2017_to_2022.csv")

# Preview the first few rows of the dataset
head(chicago_crimes)
```
*** Pre covid***
```{r}
# Users -> wards
# Pages -> Primary types
# Determine the top primary types
top_primary_types <- chicago_crimes %>%
  count(`Primary Type`) %>%
  arrange(n) %>%
  slice_head(n = 10) %>%
  pull(`Primary Type`)

# Filter the data to include only the top primary types
tb_ward_primaryType <- chicago_crimes %>%
  filter(`Primary Type` %in% top_primary_types) %>%
  filter(YearMonth < "2020-04-01") %>%
  select(Ward, `Primary Type`)

#tb_ward_primaryType <- chicago_crimes %>% select(Ward, `Primary Type`)
```

Top 3 Types of Crime
```{r}
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3)
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3) %>% pull(`Primary Type`)
```
***Recommendation using Clustering***

Clustering

```{r}
# Matrix that has on each row a Ward(user) and for each Ward
# the information on number of crime; this can be obtained with the table() function
dat <- table(tb_ward_primaryType$Ward, tb_ward_primaryType$`Primary Type`)

# function dist() to obtain a distance matrix with the Euclidean distance between the wards;
dm <- dist(dat) # By default uses euclidean distance
#dm

# function hclust() with the distance matrix to obtain an agglomerative clustering model of this data
cl <- hclust(dm)

# Visualize the obtained dendogram with function plot()
plot(cl)
plot(cl, hang=-0.1)


# use the function cutree() to ”cut” the hierarchical clustering in just two clusters; inspect the cluster membership of each user
cm <- cutree(cl, 3)

# use the function rect.hclust() to draw the previous solution in thedendogram
rect.hclust(cl, 3)


```
Analyze cluster 1
```{r}
# Add the clusters attribute
tb_ward_primaryType_c <- mutate(tb_ward_primaryType, cluster = cm[tb_ward_primaryType$Ward])

# inspect what were the crimes in cluster 1
# select crimes that belong to the cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```

Analyze cluster 2
```{r}
# inspect what were the crimes in cluster 2
# select crimes that belong to the cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```
Analyze cluster 3
```{r}
# inspect what were the crimes in cluster 3
# select crimes that belong to the cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)
```
***Recommendation using Association Rules***
```{r}
# Coercing the data frame with ward-primary_type access information to a binaryRatingMatrix (brm)
brm <- as(as.data.frame(tb_ward_primaryType), "binaryRatingMatrix")
brm
```

```{r}
# select the information on the first 42 Wards to be used as training offline data and save it to a new variable (e.g brm_offline)
brm_offline <- brm[1:50]
brm_offline
# checking the data frame
getData.frame(brm_offline)
# The information about the data structure
getRatingMatrix(brm_offline)
# The best way to 'look' at rating matrices
#inspect(getRatingMatrix(brm_offline))
```

```{r}
r <- rowCounts(brm_offline)
r
```

```{r}
c <- colCounts(brm_offline)
c
```


```{r}
image(brm_offline)
```


```{r}
# obtain the recommender model based on association 
modelAR <- Recommender(brm_offline, "AR") # AR = Association Rules

#6 g)
# check the model
getModel(modelAR)

# A -> B
# lhs -> rhs (left end side -> right end side)

rules <- getModel(modelAR)$rule_base
inspect(subset(rules, confidence > 0.9 & support > 0.6))
#inspect(rules)
```

*** Pos covid***


```{r}
# Users -> wards
# Pages -> Primary types
# Determine the top primary types
top_primary_types <- chicago_crimes %>%
  count(`Primary Type`) %>%
  arrange(n) %>%
  slice_head(n = 10) %>%
  pull(`Primary Type`)

# Filter the data to include only the top primary types
tb_ward_primaryType <- chicago_crimes %>%
  filter(`Primary Type` %in% top_primary_types) %>%
  filter(YearMonth >= "2020-04-01") %>%
  select(Ward, `Primary Type`)

#tb_ward_primaryType <- chicago_crimes %>% select(Ward, `Primary Type`)
```

Top 3 Types of Crime
```{r}
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3)
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3) %>% pull(`Primary Type`)
```


***Recommendation using Clustering***

Clustering

```{r}
# Matrix that has on each row a Ward(user) and for each Ward
# the information on number of crime; this can be obtained with the table() function
dat <- table(tb_ward_primaryType$Ward, tb_ward_primaryType$`Primary Type`)

# function dist() to obtain a distance matrix with the Euclidean distance between the wards;
dm <- dist(dat) # By default uses euclidean distance
#dm

# function hclust() with the distance matrix to obtain an agglomerative clustering model of this data
cl <- hclust(dm)

# Visualize the obtained dendogram with function plot()
plot(cl)
plot(cl, hang=-0.1)


# use the function cutree() to ”cut” the hierarchical clustering in just two clusters; inspect the cluster membership of each user
cm <- cutree(cl, 3)

# use the function rect.hclust() to draw the previous solution in thedendogram
rect.hclust(cl, 3)


```


Analyze cluster 1
```{r}
# Add the clusters attribute
tb_ward_primaryType_c <- mutate(tb_ward_primaryType, cluster = cm[tb_ward_primaryType$Ward])

# inspect what were the crimes in cluster 1
# select crimes that belong to the cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```



Analyze cluster 2
```{r}
# inspect what were the crimes in cluster 2
# select crimes that belong to the cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```


Analyze cluster 3
```{r}
# inspect what were the crimes in cluster 3
# select crimes that belong to the cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)
```


***Recommendation using Association Rules***
```{r}
# Coercing the data frame with ward-primary_type access information to a binaryRatingMatrix (brm)
brm <- as(as.data.frame(tb_ward_primaryType), "binaryRatingMatrix")
brm
```

```{r}
# select the information on the first 42 Wards to be used as training offline data and save it to a new variable (e.g brm_offline)
brm_offline <- brm[1:50]
brm_offline
# checking the data frame
getData.frame(brm_offline)
# The information about the data structure
getRatingMatrix(brm_offline)
# The best way to 'look' at rating matrices
#inspect(getRatingMatrix(brm_offline))
```


```{r}
r <- rowCounts(brm_offline)
r
```

```{r}
c <- colCounts(brm_offline)
c
```


```{r}
image(brm_offline)
```


```{r}
# obtain the recommender model based on association 
modelAR <- Recommender(brm_offline, "AR") # AR = Association Rules

#6 g)
# check the model
getModel(modelAR)

# A -> B
# lhs -> rhs (left end side -> right end side)

rules <- getModel(modelAR)$rule_base
inspect(subset(rules, confidence > 0.9 & support > 0.6))
#inspect(rules)
```

*** All time***


```{r}
# Users -> wards
# Pages -> Primary types
# Determine the top primary types
top_primary_types <- chicago_crimes %>%
  count(`Primary Type`) %>%
  arrange(n) %>%
  slice_head(n = 10) %>%
  pull(`Primary Type`)

# Filter the data to include only the top primary types
tb_ward_primaryType <- chicago_crimes %>%
  filter(`Primary Type` %in% top_primary_types) %>%
  select(Ward, `Primary Type`)

#tb_ward_primaryType <- chicago_crimes %>% select(Ward, `Primary Type`)
```

Top 3 Types of Crime
```{r}
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3)
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3) %>% pull(`Primary Type`)
```


***Recommendation using Clustering***

Clustering

```{r}
# Matrix that has on each row a Ward(user) and for each Ward
# the information on number of crime; this can be obtained with the table() function
dat <- table(tb_ward_primaryType$Ward, tb_ward_primaryType$`Primary Type`)

# function dist() to obtain a distance matrix with the Euclidean distance between the wards;
dm <- dist(dat) # By default uses euclidean distance
#dm

# function hclust() with the distance matrix to obtain an agglomerative clustering model of this data
cl <- hclust(dm)

# Visualize the obtained dendogram with function plot()
plot(cl)
plot(cl, hang=-0.1)


# use the function cutree() to ”cut” the hierarchical clustering in just two clusters; inspect the cluster membership of each user
cm <- cutree(cl, 3)

# use the function rect.hclust() to draw the previous solution in thedendogram
rect.hclust(cl, 3)


```


Analyze cluster 1
```{r}
# Add the clusters attribute
tb_ward_primaryType_c <- mutate(tb_ward_primaryType, cluster = cm[tb_ward_primaryType$Ward])

# inspect what were the crimes in cluster 1
# select crimes that belong to the cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```



Analyze cluster 2
```{r}
# inspect what were the crimes in cluster 2
# select crimes that belong to the cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```


Analyze cluster 3
```{r}
# inspect what were the crimes in cluster 3
# select crimes that belong to the cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)
```


***Recommendation using Association Rules***
```{r}
# Coercing the data frame with ward-primary_type access information to a binaryRatingMatrix (brm)
brm <- as(as.data.frame(tb_ward_primaryType), "binaryRatingMatrix")
brm
```

```{r}
# select the information on the first 42 Wards to be used as training offline data and save it to a new variable (e.g brm_offline)
brm_offline <- brm[1:50]
brm_offline
# checking the data frame
getData.frame(brm_offline)
# The information about the data structure
getRatingMatrix(brm_offline)
# The best way to 'look' at rating matrices
#inspect(getRatingMatrix(brm_offline))
```


```{r}
r <- rowCounts(brm_offline)
r
```

```{r}
c <- colCounts(brm_offline)
c
```


```{r}
image(brm_offline)
```


```{r}
# obtain the recommender model based on association 
modelAR <- Recommender(brm_offline, "AR") # AR = Association Rules

#6 g)
# check the model
getModel(modelAR)

# A -> B
# lhs -> rhs (left end side -> right end side)

rules <- getModel(modelAR)$rule_base
inspect(subset(rules, confidence > 0.9 & support > 0.8))
#inspect(rules)


```
*** All crimes All time***


```{r}
# Users -> wards
# Pages -> Primary types
# Determine the top primary types

tb_ward_primaryType <- chicago_crimes %>% select(Ward, `Primary Type`)
```

Top 3 Types of Crime
```{r}
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3)
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3) %>% pull(`Primary Type`)
```


***Recommendation using Clustering***

Clustering

```{r}
# Matrix that has on each row a Ward(user) and for each Ward
# the information on number of crime; this can be obtained with the table() function
dat <- table(tb_ward_primaryType$Ward, tb_ward_primaryType$`Primary Type`)

# function dist() to obtain a distance matrix with the Euclidean distance between the wards;
dm <- dist(dat) # By default uses euclidean distance
#dm

# function hclust() with the distance matrix to obtain an agglomerative clustering model of this data
cl <- hclust(dm)

# Visualize the obtained dendogram with function plot()
plot(cl)
plot(cl, hang=-0.1)


# use the function cutree() to ”cut” the hierarchical clustering in just two clusters; inspect the cluster membership of each user
cm <- cutree(cl, 3)

# use the function rect.hclust() to draw the previous solution in thedendogram
rect.hclust(cl, 3)


```


Analyze cluster 1
```{r}
# Add the clusters attribute
tb_ward_primaryType_c <- mutate(tb_ward_primaryType, cluster = cm[tb_ward_primaryType$Ward])

# inspect what were the crimes in cluster 1
# select crimes that belong to the cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```



Analyze cluster 2
```{r}
# inspect what were the crimes in cluster 2
# select crimes that belong to the cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```


Analyze cluster 3
```{r}
# inspect what were the crimes in cluster 3
# select crimes that belong to the cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)
```


***Recommendation using Association Rules***
```{r}
# Coercing the data frame with ward-primary_type access information to a binaryRatingMatrix (brm)
brm <- as(as.data.frame(tb_ward_primaryType), "binaryRatingMatrix")
brm
```

```{r}
# select the information on the first 42 Wards to be used as training offline data and save it to a new variable (e.g brm_offline)
brm_offline <- brm[1:50]
brm_offline
# checking the data frame
getData.frame(brm_offline)
# The information about the data structure
getRatingMatrix(brm_offline)
# The best way to 'look' at rating matrices
#inspect(getRatingMatrix(brm_offline))
```


```{r}
r <- rowCounts(brm_offline)
r
```

```{r}
c <- colCounts(brm_offline)
c
```


```{r}
image(brm_offline)
```


```{r}
# obtain the recommender model based on association 
modelAR <- Recommender(brm_offline, "AR") # AR = Association Rules

#6 g)
# check the model
getModel(modelAR)

# A -> B
# lhs -> rhs (left end side -> right end side)

rules <- getModel(modelAR)$rule_base
#inspect(subset(rules, confidence == 1 & support == 1))
#inspect(rules)


```
*** All crimes pos covid***


```{r}
# Users -> wards
# Pages -> Primary types
# Determine the top primary types

tb_ward_primaryType <- chicago_crimes %>% 
  filter(YearMonth >= "2020-04-01") %>%
  select(Ward, `Primary Type`)
```

Top 3 Types of Crime
```{r}
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3)
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3) %>% pull(`Primary Type`)
```


***Recommendation using Clustering***

Clustering

```{r}
# Matrix that has on each row a Ward(user) and for each Ward
# the information on number of crime; this can be obtained with the table() function
dat <- table(tb_ward_primaryType$Ward, tb_ward_primaryType$`Primary Type`)

# function dist() to obtain a distance matrix with the Euclidean distance between the wards;
dm <- dist(dat) # By default uses euclidean distance
#dm

# function hclust() with the distance matrix to obtain an agglomerative clustering model of this data
cl <- hclust(dm)

# Visualize the obtained dendogram with function plot()
plot(cl)
plot(cl, hang=-0.1)


# use the function cutree() to ”cut” the hierarchical clustering in just two clusters; inspect the cluster membership of each user
cm <- cutree(cl, 3)

# use the function rect.hclust() to draw the previous solution in thedendogram
rect.hclust(cl, 3)


```


Analyze cluster 1
```{r}
# Add the clusters attribute
tb_ward_primaryType_c <- mutate(tb_ward_primaryType, cluster = cm[tb_ward_primaryType$Ward])

# inspect what were the crimes in cluster 1
# select crimes that belong to the cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```



Analyze cluster 2
```{r}
# inspect what were the crimes in cluster 2
# select crimes that belong to the cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```


Analyze cluster 3
```{r}
# inspect what were the crimes in cluster 3
# select crimes that belong to the cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)
```


***Recommendation using Association Rules***
```{r}
# Coercing the data frame with ward-primary_type access information to a binaryRatingMatrix (brm)
brm <- as(as.data.frame(tb_ward_primaryType), "binaryRatingMatrix")
brm
```

```{r}
# select the information on the first 42 Wards to be used as training offline data and save it to a new variable (e.g brm_offline)
brm_offline <- brm[1:50]
brm_offline
# checking the data frame
getData.frame(brm_offline)
# The information about the data structure
getRatingMatrix(brm_offline)
# The best way to 'look' at rating matrices
#inspect(getRatingMatrix(brm_offline))
```


```{r}
r <- rowCounts(brm_offline)
r
```

```{r}
c <- colCounts(brm_offline)
c
```


```{r}
image(brm_offline)
```

*** All crimes pre covid***


```{r}
# Users -> wards
# Pages -> Primary types
# Determine the top primary types

tb_ward_primaryType <- chicago_crimes %>% 
  filter(YearMonth < "2020-04-01") %>%
  select(Ward, `Primary Type`)
```

Top 3 Types of Crime
```{r}
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3)
tb_ward_primaryType %>% group_by(`Primary Type`) %>% tally(sort = TRUE) %>% top_n(3) %>% pull(`Primary Type`)
```


***Recommendation using Clustering***

Clustering

```{r}
# Matrix that has on each row a Ward(user) and for each Ward
# the information on number of crime; this can be obtained with the table() function
dat <- table(tb_ward_primaryType$Ward, tb_ward_primaryType$`Primary Type`)

# function dist() to obtain a distance matrix with the Euclidean distance between the wards;
dm <- dist(dat) # By default uses euclidean distance
#dm

# function hclust() with the distance matrix to obtain an agglomerative clustering model of this data
cl <- hclust(dm)

# Visualize the obtained dendogram with function plot()
plot(cl)
plot(cl, hang=-0.1)


# use the function cutree() to ”cut” the hierarchical clustering in just two clusters; inspect the cluster membership of each user
cm <- cutree(cl, 3)

# use the function rect.hclust() to draw the previous solution in thedendogram
rect.hclust(cl, 3)


```


Analyze cluster 1
```{r}
# Add the clusters attribute
tb_ward_primaryType_c <- mutate(tb_ward_primaryType, cluster = cm[tb_ward_primaryType$Ward])

# inspect what were the crimes in cluster 1
# select crimes that belong to the cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 1
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 1) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```



Analyze cluster 2
```{r}
# inspect what were the crimes in cluster 2
# select crimes that belong to the cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 2
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 2) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)

```


Analyze cluster 3
```{r}
# inspect what were the crimes in cluster 3
# select crimes that belong to the cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% select(`Primary Type`)
# Count the number of crimes per ward in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally()
# Obtain the top 5 Types of crime in cluster 3
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5)
filter(tb_ward_primaryType_c, cluster == 3) %>% group_by(`Primary Type`) %>% tally(sort=TRUE) %>% top_n(5) %>% pull(`Primary Type`)
```

